### 2016-06-02 exam2.tex
started sketching scope and rearranging

Large datasets of climate and weather data are being produced from multiple sources. With cheaper and increased computer power, and cheaper disk storage, it is now possible to more easily create long model simulations at higher resolutions. Increasingly  high 
resolution satellite data and reanalysis projects which blend both model prediction and measurements create readily available large uniformly sampled spatio-temporal resolution datasets. Measured data from networks of ground stations and proxy data from trees, 
glaciers, oceans, corals, fossils, and historical records are also becoming more accessible, 
yielding sometimes irregularly sampled data that provides a host of 
information on climate variability. The great size of many of these data sets mean that just providing a download link does not really make the data accessible to the public or even other scientists. It is important for the scientists who produce the data to have a way to make it explorable..

>>>>

%Large datasets of climate and weather data are being produced from multiple sources. With cheaper and increased computer power, and cheaper disk storage, it is now possible to more easily create long model simulations at higher resolutions. Increasingly  high 
%resolution satellite data and reanalysis projects which blend both model prediction and measurements create readily available large uniformly sampled spatio-temporal resolution datasets. Measured data from networks of ground stations and proxy data from trees, 
%glaciers, oceans, corals, fossils, and historical records are also becoming more accessible, 
%yielding sometimes irregularly sampled data that provides a host of 
%information on climate variability. The great size of many of these data sets mean that just providing a download link does not really make the data accessible to the public or even other scientists. It is important for the scientists who produce the data to have a way to make it explorable..

\subsection{Scope}

This paper focuses on the visualization of:
\begin{itemize}
\item climate and weather data - observational and model
\item has both a spaitial and temporal component
\item requires aggregation(ML or stats) before can be visualized with simple viz (line, bar, pie, scatter, heatmap)
\end{itemize}
